Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-01 EconGrowth.Rnw
Attempting to draw a parameters graph for the CD model. Not working yet.

cobbDouglasCountryRowsForParamsGraph <- function(countryName){
  dataCD <- cobbDouglasData(countryName)
  #Create three rows, one for each parameter.
  lambdaRow <- cbind(dataCD["- 95% CI", "lambda"], 
                     dataCD["CD", "lambda"], 
                     dataCD["+ 95% CI", "lambda"], 
                     countryName, 
                     "lambda")
  alphaRow <- cbind(dataCD["- 95% CI", "alpha"],
                    dataCD["CD", "alpha"],  
                    dataCD["+ 95% CI", "alpha"],
                    countryName,
                    "alpha")
  betaRow <- cbind(dataCD["- 95% CI", "beta"],   
                   dataCD["CD", "beta"],   
                   dataCD["+ 95% CI", "beta"],
                   countryName,
                   "beta")
  #Now combine into a table
  table <- rbind(lambdaRow, alphaRow, betaRow)
  colnames(table) <- c("- 95% CI", "value", "+ 95% CI", "country", "parameter")
  return(table)
}

############################
# Aggregates the Cobb-Douglas results into a big data table
##
cobbDouglasParamsTable <- function(){
  dataCD <- rbind(cobbDouglasCountryRow("US"),
                cobbDouglasCountryRow("UK"),
                cobbDouglasCountryRow("JP"),
                cobbDouglasCountryRow("CN"),
                cobbDouglasCountryRow("ZA"),
                cobbDouglasCountryRow("SA"),
                cobbDouglasCountryRow("IR"),
                cobbDouglasCountryRow("TZ"),
                cobbDouglasCountryRow("ZM"))
  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
                        " ", "$\\alpha$",  " ",
                        " ", "$\\beta$",   " ")
  rownames(dataCD) <- countryAbbrevs
  tableCD <- xtable(dataCD, 
                    caption="Cobb-Douglas parameters for 1980-2011 (US, UK, JP) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence bounds to left and right.)", 
                    digit = c(1, 4,4,4, 2,2,2, 2,2,2),
                    align = "r|ccc|ccc|ccc")
  return(tableCD)
}
@

@@

<<CD_Params_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) model parameters.">>=
createCDParamsGraph <- function(){
  # Create the data table that we want. This table has the following columns
  # -95% CI, value, +95% CI, country abbrev, parameter (lambda, alpha, or beta)
  dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))

  print(dataTable)

  graph <- segplot(value ~ country | parameter, centers=value, data=dataTable)  
  return(graph)

}

createCDParamsGraph()

@

@@

<<CDq analysis, eval=FALSE>>=
# Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
CDqTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="Q")
@

<<CDq Results, results='asis', echo=TRUE, eval=FALSE>>=
print(CDqTables[["US"]], caption.placement="top")
print(CDqTables[["ZA"]], caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCDe, sanitize.text.function = function(x){x})

@@

<<CDx analysis, eval=FALSE>>=
# Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
CDxTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="X")
@

<<CDx Results, results='asis', eval=FALSE>>=
print(CDxTables[["US"]], caption.placement="top")
print(CDxTables[["ZA"]], caption.placement="top")
@

@@

<<CDu analysis, eval=FALSE>>=
CDuTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="U")
@

<<CDu Results, results='asis', eval=FALSE>>=
print(CDuTables[["US"]], caption.placement="top")
print(CDuTables[["ZA"]], caption.placement="top")
@

@@

<<CES function>>=
cesData <- function(countryName, energyType){
  energyColumnName <- paste("i", energyType, sep="")
  # Load the data that we need.
  dataTable <- loadData(countryName)

@@

\subsection{CES with $Q$}
<<CESq analysisQ, eval=FALSE>>=
countryName <- "US"
energyType <- "Q"
tableCESq <- cesTable(countryName, energyType)

@@

<<CESq Results, results='asis', eval=FALSE>>=
print(tableCESq, caption.placement="top")

>>>>

###########################################
# Creates a number of rows in a data.frame that contain information 
# about the coefficients of a Cobb-Douglas model for countryName.
# Each parameter has its own row with confidence intervals.
# The country name is in a column. Which parameter is involved is
# also in a column.
# 
# The return type is a data.frame.
##
cobbDouglasCountryRowsForParamsGraph <- function(countryName){
  dataCD <- cobbDouglasData(countryName)
  #Create three rows, one for each parameter.
  lambdaRow <- cbind(countryName,
                     "lambda",
                     dataCD["- 95% CI", "lambda"], 
                     dataCD["CD", "lambda"], 
                     dataCD["+ 95% CI", "lambda"])
  alphaRow <- cbind(countryName, 
                    "alpha",
                    dataCD["- 95% CI", "alpha"],
                    dataCD["CD", "alpha"],  
                    dataCD["+ 95% CI", "alpha"])
  betaRow <- cbind(countryName, 
                   "beta",
                   dataCD["- 95% CI", "beta"],   
                   dataCD["CD", "beta"],   
                   dataCD["+ 95% CI", "beta"])
  #Now combine into a table. table is a matrix, not a data.frame.
  table <- rbind(lambdaRow, alphaRow, betaRow)
  #Set names for the columns
  colnames(table) <- c("country", "parameter", "lowerCI", "value", "upperCI")
  #Convert the matrix to a data.frame and return it.
  return(data.frame(table))
}

############################
# Aggregates the Cobb-Douglas results into a big data table
##
cobbDouglasParamsTable <- function(){
  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow))
  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
                        " ", "$\\alpha$",  " ",
                        " ", "$\\beta$",   " ")
  rownames(dataCD) <- countryAbbrevs
  tableCD <- xtable(dataCD, 
                    caption="Cobb-Douglas parameters for 1980-2011 (US, UK, JP) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence bounds to left and right.)", 
                    digit = c(1, 4,4,4, 2,2,2, 2,2,2),
                    align = "r|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
  return(tableCD)
}
@

@@

<<CD_Params_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) model parameters.">>=
createCDParamsGraph <- function(){
  # Create a data table with the following columns:
  # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
  dataTable <- do.call("rbind", 
                       lapply(countryAbbrevs, 
                              cobbDouglasCountryRowsForParamsGraph))
  print(class(dataTable))
  print(dataTable)
  # Make a graph. I want the following:
  ### two-letter country abbreviation on the horizontal axis
  ### dots for the values of each parameter
  ### error bars to the top and bottom of the dots representing the 95% CI
  ### three panels, one for each parameter (lambda, alpha, and beta)
  #
  # Note that "segplot" is in the "latticeExtra" package.
  # But, at this point, I obtain the following error:
  # "Error:  range not meaningful for factors"
  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                   data = dataTable, 
                   centers = value)
  return(graph)
}
createCDParamsGraph()
@

@@

<<CDq analysis, echo=FALSE, eval=FALSE>>=
# Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
CDqTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="Q")
@

<<CDq Results, results='asis', echo=FALSE, eval=FALSE>>=
print(CDqTables[["US"]], caption.placement="top")
print(CDqTables[["ZA"]], caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCDe, sanitize.text.function = function(x){x})

@@

<<CDx analysis, echo=FALSE, eval=FALSE>>=
# Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
CDxTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="X")
@

<<CDx Results, results='asis', echo=FALSE, eval=FALSE>>=
print(CDxTables[["US"]], caption.placement="top")
print(CDxTables[["ZA"]], caption.placement="top")
@

@@

<<CDu analysis, echo=FALSE, eval=FALSE>>=
CDuTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="U")
@

<<CDu Results, results='asis', echo=FALSE, eval=FALSE>>=
print(CDuTables[["US"]], caption.placement="top")
print(CDuTables[["ZA"]], caption.placement="top")
@

@@

<<CES function, echo=FALSE, eval=FALSE>>=
cesData <- function(countryName, energyType){
  energyColumnName <- paste("i", energyType, sep="")
  # Load the data that we need.
  dataTable <- loadData(countryName)

@@

\subsection{CES with $Q$}
<<CESq analysisQ, echo=FALSE, eval=FALSE>>=
countryName <- "US"
energyType <- "Q"
tableCESq <- cesTable(countryName, energyType)

@@

<<CESq Results, results='asis', echo=FALSE, eval=FALSE>>=
print(tableCESq, caption.placement="top")
